Contention Management for 5G

### 2017-02-01 article/article.tex

@@

\section{Proposed Solutions, solving PALL}

@@

  \subsection{No waiting times}
    \subsubsection{Shortest-longest}
      \paragraph{Algo}
      \paragraph{Period}
    \subsubsection{Greedy Algorithm with higher bound}
      \paragraph{Algo}
	Todo
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.N$, if we have N routes.\\
	Suppose that we have a period of $3.\tau.N$ slots, divided in $\tau$ macro-slots.
    \subsubsection{Exhaustive generation}
      Décrire l'algo, expliquer les coupes
    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.

@@

>>>>

    \scalebox{0.5}{

    \begin{tikzpicture}

    \tikzset{
      LabelStyle/.style = { rectangle, rounded corners, draw,
			  font = \bfseries },
      EdgeStyle/.append style = {->} }
      \SetGraphUnit{5}
      \Vertex[x=4,y=2]{s3}
      \Vertex[x=0,y=4]{s2}
      \Vertex[x=0,y=6]{s1}

      \Vertex[x=12,y=3]{l3}
      \Vertex[x=14,y=4]{l2}
      \Vertex[x=10,y=2]{l1}
      \tikzstyle{VertexStyle}=[shape = circle, draw, minimum size = 20pt]
	\tikzset{
      VertexStyle/.append style = {blue} }
	\Vertex[x=-8,y=3]{1}
	      \tikzset{
      VertexStyle/.append style = {green} }
	  \Vertex[x=-7,y=5]{2}

	    \tikzset{
      VertexStyle/.append style = {red} }
	  \Vertex[x=-6,y=4]{3}
		\tikzset{
      VertexStyle/.append style = {black} }

      \SetVertexNoLabel
      \Vertex[x=2,y=5]{A}
      \Vertex[x=4,y=5]{B}
      \Vertex[x=10,y=5]{C}
      \Vertex[x=12,y=5]{D}
      \Vertex[x=6,y=3]{E}
      \Vertex[x=8,y=3]{F}
      \tikzset{
      EdgeStyle/.append style = {green} }
      \Edge[label = 3](s2)(A)
      \Edge(A)(B)
      \Edge(B)(C)
      \Edge(C)(D)
      \Edge(D)(l2)

      \tikzset{
      EdgeStyle/.append style = {red} }
      \Edge[label = 1](s3)(E)
      \Edge(E)(F)
      \Edge(F)(l3) 
	\tikzset{
      EdgeStyle/.append style = {blue} }
      \Edge[label = 1](s1)(A)
      \Edge[label = 1](A)(B)
      \Edge[label = 1](B)(E)
      \Edge(E)(F)
      \Edge(F)(l1)

	\tikzset{
      EdgeStyle/.append style = {black,-} }

      \Edge(1)(2)
      \Edge(1)(3)
    \node (1) at (-3,4){\Huge $\rightarrow$};
    \end{tikzpicture}

    }

@@

\section{The Star Topolgy}

@@

  \subsection{No waiting times}
    \subsubsection{Shortest-longest}
      \paragraph{Algo}
      \paragraph{Period}
    \subsubsection{Greedy Algorithm with higher bound}

	\begin{algorithm}[H]
	\caption{Greedy with Higher bound Period(GHP)}
	\begin{algorithmic}
	\REQUIRE ${\cal R}_{\cal C}$, period $P$
	\ENSURE A P-periodic affectation in p $\leq P$, or FAILURE
	\STATE $P1[P]$ slots of size $\tau$ in first way period.
	\STATE $P2[P]$ slots  of size $\tau$ in back way period.
	\FORALL{route i in ${\cal R}_{\cal C}$ }

	\FORALL{slot j in P1}

	\IF{$P1[j]$ is free, and the corresponding slot(s) in P2 are free}

	\STATE $o_i \leftarrow j$
	\ENDIF

	\IF{No intervals are found for i}
	\STATE return FAILURE
	\ENDIF
	\ENDFOR

	\ENDFOR

	\end{algorithmic}
	\end{algorithm}
      \paragraph{Period}
	This algorithm gives us a solution without waiting times in a maximum period $3.\tau.c$, if we have $c$ routes.\\
	Suppose that we have a period of $3.\tau.c$ slots, divided in $\tau$ macro-slots. Let us call {\em forward period} the period in the central node when the messages goes to RRH to BBU, and {\em backward period} the period when the messages comes back in the other way. Put a message in the first slot of size $\tau$ in the forward period, such that the corresponding area in the backward period is free.This message takes at most 2 slots of time $\tau$ in the backward period.\\
	\todo{Dessin qui illustre ça}\\
	When $k < c$ messages are put in the forward period, and we want to add another message, there is $3.c - k$ free slots of size $\tau$ in the forward period. Those $3.c - k$ gives us $3.c - k$ possible slots in the backward periods.\\
	The $k$ messages uses at most $2k$ slots of size $\tau$ used in the backward period. Since $k<c$,  $2k < 3.c - k$, thus using the pigeonhole principle, there is at least one free slot in the backward period for the new message.

    \subsubsection{Exhaustive generation}
      Décrire l'algo, expliquer les coupes
    \subsubsection{Results}
      Resultats des simulations : Shortest-longest optimal pour ces parametres.

@@

\bibliographystyle{plain}
\bibliography{Sources.bib}
